Efficient ancestry and mutation simulation with msprime 1.0

### 2022-01-06 paper.tex
remove columnwidth; closes #265
No affiliation -> Independent Researcher
different shared author statements

% Bjarki
\affil[9]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin, 10115, Germany }
% Castedo
\affil[10]{Fresh Pond Research Institute, Cambridge, MA 02140, USA}
% Jared, Murillo, Peter, Andy
\affil[11]{Institute of Ecology and Evolution, Department of Biology, University of Oregon, OR 97403-5289, USA}
% Jared
\affil[12]{Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA 98102, USA}
% Ariella
\affil[13]{Department of Genetics, University of North Carolina at Chapel Hill, NC 27599-7264, USA}
\affil[14]{Embark Veterinary, Inc., Boston, MA 02111, USA}
% Gregor
\affil[15]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
% Bing
\affil[16]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD, 21201, USA}
% Winni
\affil[17]{Center for Hematology and Regenerative Medicine, Karolinska Institute, 141 83 Huddinge, Sweden}
% Michael
\affil[18]{Natural History Museum, University of Oslo, Blindern 0318 Oslo, Norway}
% Simon, Dom, Ivan
\affil[19]{Department of Human Genetics, McGill University, Montr\'eal, QC H3A 0C7, Canada}
% Nathaniel
\affil[20]{Department of Entomology, Pennsylvania State University, PA 16802, USA}
% Consuelo
\affil[21]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[22]{IIT Bombay, Powai, Mumbai 400 076, Maharashtra, India}
% Thibaut
\affil[23]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich, 85354 Freising, Germany}
% Kevin
\affil[24]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
% Hugo
\affil[25]{No affiliation}
% Jere
\affil[26]{Department of Statistics, University of Warwick, CV4 7AL, UK}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon, OR 97403-5289 USA}

@@

% Use the \equalcontrib command to mark authors with equal
% contributions, using the relevant superscript numbers
% \equalcontrib{1}
% \equalcontrib{2}
\equalcontrib{$\star$} % {Denotes shared first authorship, listed alphabetically}
\equalcontrib{$\dagger$} % {Denotes shared senior authorship, listed alphabetically}
% \equalcontrib{$\ddagger$}{Denotes corresponding author}

@@

\begin{figure}
    \includegraphics{figures/mutations-perf}
\caption{\label{fig-mutations-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We ran 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.
\the\columnwidth}
\end{figure}

>>>>

% Bjarki
\affil[9]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin, 10115, Germany }
% Castedo
\affil[10]{Fresh Pond Research Institute, Cambridge, MA 02140, USA}
% Jared, Murillo, Peter, Andy
\affil[11]{Institute of Ecology and Evolution, Department of Biology, University of Oregon, OR 97403-5289, USA}
% Jared
\affil[12]{Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA 98102, USA}
% Ariella
\affil[13]{Department of Genetics, University of North Carolina at Chapel Hill, NC 27599-7264, USA}
\affil[14]{Embark Veterinary, Inc., Boston, MA 02111, USA}
% Gregor
\affil[15]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
% Bing
\affil[16]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD, 21201, USA}
% Winni
\affil[17]{Center for Hematology and Regenerative Medicine, Karolinska Institute, 141 83 Huddinge, Sweden}
% Michael
\affil[18]{Natural History Museum, University of Oslo, Blindern 0318 Oslo, Norway}
% Simon, Dom, Ivan
\affil[19]{Department of Human Genetics, McGill University, Montr\'eal, QC H3A 0C7, Canada}
% Nathaniel
\affil[20]{Department of Entomology, Pennsylvania State University, PA 16802, USA}
% Consuelo
\affil[21]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[22]{IIT Bombay, Powai, Mumbai 400 076, Maharashtra, India}
% Thibaut
\affil[23]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich, 85354 Freising, Germany}
% Kevin
\affil[24]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
% Hugo
\affil[25]{Independent Researcher}
% Jere
\affil[26]{Department of Statistics, University of Warwick, CV4 7AL, UK}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon, OR 97403-5289 USA}

@@

% Use the \equalcontrib command to mark authors with equal
% contributions, using the relevant superscript numbers
% \equalcontrib{1}
% \equalcontrib{2}
\makeatletter
\newcommand{\equalcontribfirst}[1]{\@authfootnote{#1}{These authors contributed equally to this work, as joint first authors.}}
\newcommand{\equalcontriblast}[1]{\@authfootnote{#1}{These authors contributed equally to this work, as joint last authors.}}
\makeatother

\equalcontribfirst{$\star$} % {Denotes shared first authorship, listed alphabetically}
\equalcontriblast{$\dagger$} % {Denotes shared senior authorship, listed alphabetically}
% \equalcontrib{$\ddagger$}{Denotes corresponding author}

@@

\begin{figure}
    \includegraphics{figures/mutations-perf}
\caption{\label{fig-mutations-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We ran 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.
}
\end{figure}
